Assault Rate Trends Within and Around the University of Toronto: A Ten-Year Analysis

### 2024-01-23 outputs/paper/paper.qmd
commiting all my work thus far in paper.qmd.

## Load packages
library(tidyverse)
library(knitr)
library(ggplot2)
library(readr)

@@

##Results

>>>>

## Load packages
library(tidyverse)
library(knitr)
library(ggplot2)
library(readr)
library(dplyr)
library(tidyr)

@@

##Results
###Assault Rates per University of Toronto Neighbourhood 
Over the past decade University of Toronto's encompassing neighbourhoods have exhibited unique trends in assault rates. "Kensington-Chinatown" shows a erratic pattern, peaking around 2018 followed by a sharp decline in 2019 and a subsequent rise again. "The Annex" demonstrates a generally consitent, however, slight upward trend. Both "Bay-Cloverhill" and "University" show quite inconsistent patterns with several fluctuations over the ten year time span. What is most notable is Universities steady increase from 2020 on. (\@ref(fig-assaults_per_year_uoft)) shows the assault rates per year for each University of Toronto neighbourhood.
```{r}
#| message: false
#| echo: false
#| label: fig-assaults_per_year_uoft
#| fig-cap: Assault Rates per year in University of Toronto Neighbourhoods (2014-2023)

long_data <- cleaned_data |>
  gather(key = "Year", value = "Assault_Rate", -Neighbourhood) |>
  mutate(Year = as.numeric(str_replace(Year, "ASSAULT_RATE_", "")))

# Plot the graph
ggplot(long_data, aes(x = Year, y = Assault_Rate, group = Neighbourhood, color = Neighbourhood)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(
    title = "Assault Rates in University of Toronto Neighbourhoods (2014-2023)",
    x = "Year",
    y = "Assault Rate",
    color = "Neighbourhood"
  ) +
  ylim(500, 2500) # Adjust these values based on your data's range

```

###Assault Rates per Neighbourhood in the Surrounding Areas
```{r}
#| message: false
#| echo: false
#| label: fig-assaults_per_year_uoft
#| fig-cap: Assault Rates per year in University of Toronto Neighbourhoods (2014-2023)

long_data <- surrounding_neighbourhoods %>%
  gather(key = "Year", value = "Assault_Rate", -Neighbourhood) %>%
  mutate(Year = as.numeric(str_extract(Year, "\\d{4}")))

# Check for NA values in Year
sum(is.na(long_data$Year))

# Plot the graph
ggplot(long_data, aes(x = Year, y = Assault_Rate, group = Neighbourhood, color = Neighbourhood)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(
    title = "Assault Rates in Surrounding University of Toronto Neighbourhoods (2014-2023)",
    x = "Year",
    y = "Assault Rate",
    color = "Neighbourhood"
  ) +
  scale_x_continuous(breaks = 2014:2023) # Make sure the breaks include all years in your data

```
